Certified Knowledge Compilation \\ with Application to Verified Model Counting

### 2023-03-09 doc/mc-data.tex

\documentclass{llncs}
\usepackage{latexsym}
\usepackage{times}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{cite}
\usepackage{booktabs}
\usepackage{adjustbox}
\usepackage{marvosym}
%% Colored hyperlink 
\newcommand{\hcref}[1]{\texttt{\small\url{#1}}}

\bibliographystyle{splncs04}
%\bibliographystyle{abbrv}

\title{Validated Model Counting Data \\ Version of \today}

\author{Randal E. Bryant}

\authorrunning{R. E. Bryant}

\titlerunning{Validated Model Counting}

\institute{
Computer Science Department \\
Carnegie Mellon University, Pittsburgh, PA, United States
}

@@

\section*{Methodology}
\begin{enumerate}
   \item Retrieved 200 public model counting benchmarks from 2022 Model Counting Competition website
     \begin{center}
       \hcref{https://mccompetition.org/2022/mc\_description.html}
     \end{center}
     \begin{itemize}
     \item 100 public instances from Track 1 (unweighted model counting)
     \item 100 public instances from Track 2 (weighted model counting)
     \end{itemize}
   \item Removed duplicates
     \begin{itemize}
    \item  20 instances were duplicated in the two tracks
     \item Reduces set of benchmarks to 180
     \end{itemize}
   \item Ran D4 on 180 instances with time limit of 4000 seconds
     \begin{itemize}
     \item Completed for 124 instances
     \end{itemize}
   \item Generated POG representations from dDNNF graphs
     \begin{itemize}
     \item Simplifications via constant propagation
       \begin{itemize}
       \item Number of POG nodes around $0{.}90\times$ number of dDNNF nodes
       \end{itemize}
     \item Used heuristics to identify root node, and then put in topological order with root node at end.
     \item Measure complexity by number of defining clauses $D$
       \begin{itemize}
       \item Product or sum node with degree $k$ requires $k+1$ clauses
       \item $D$ also equals sum of number of edges and number of nodes
       \item For 124 instances, Min = 304, Median = 848,784, Mean = 93,107,937, Max = 2,761,457,765
       \end{itemize}
     \end{itemize}
   \item Ran program {\sc d2p} to generate CRAT file for maximum of 10,000 seconds
     \begin{itemize}
     \item Completed for 108 instances
     \item Exceeded clause limit for 1 instance (Our programs represent a clause ID as a 32-bit signed value)
     \item Ran out of memory for 1 instance
     \item Timed out for 14 instances
     \end{itemize}
   \item For completed CRAT files, ran {\sc crat-check} CRAT checker
     \begin{itemize}
     \item Tests all conditions for correct CRAT
     \item Most time spent performing RUP checks for clause addition and deletion
     \item Completed successfully for all 108 instances
     \item Time generally faster than {\sc d2p}. (min = 0.005, max = 1.4, harmonic mean = 0.10)
     \end{itemize}
\end{enumerate}

@@

>>>>

\documentclass[letterpaper,USenglish,cleveref, autoref, thm-restate]{lipics-v2021}
%This is a template for producing LIPIcs articles. 
%See lipics-v2021-authors-guidelines.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling cleveref support, use "cleveref"
%for enabling autoref support, use "autoref"
%for anonymousing the authors (e.g. for double-blind review), add "anonymous"
%for enabling thm-restate support, use "thm-restate"
%for enabling a two-column layout for the author/affilation part (only applicable for > 6 authors), use "authorcolumns"
%for producing a PDF according the PDF/A standard, add "pdfa"

%\pdfoutput=1 %uncomment to ensure pdflatex processing (mandatatory e.g. to submit to arXiv)
%\hideLIPIcs  %uncomment to remove references to LIPIcs series (logo, DOI, ...), e.g. when preparing a pre-final version to be uploaded to arXiv or another public repository

%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory

\usepackage{amsmath}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{booktabs}

\newcommand{\pand}{\mathbin{\land^{\sf p}}}
\newcommand{\por}{\mathbin{\lor^{\sf p}}}
\DeclareMathOperator*{\Pand}{\bigwedge^{\sf v}}
\DeclareMathOperator*{\Por}{\bigvee^{\sf a}}
\newcommand{\boolnot}{\neg}
\newcommand{\tautology}{\top}
\newcommand{\nil}{\bot}
\newcommand{\obar}[1]{\overline{#1}}
\newcommand{\oneminus}{{\sim}}
\newcommand{\lit}{\ell}

\newcommand{\varset}{X}
\newcommand{\exvarset}{Z}
\newcommand{\dependencyset}{{\cal D}}
\newcommand{\litset}{{\cal L}}
\newcommand{\ring}{{\cal R}}
\newcommand{\dset}{{\cal A}}
\newcommand{\rep}{\textbf{R}}
\newcommand{\radd}{+}
\newcommand{\rmul}{\times}
\newcommand{\addident}{\textbf{0}}
\newcommand{\mulident}{\textbf{1}}
\newcommand{\imply}{\Rightarrow}

\newcommand{\assign}{\alpha}
\newcommand{\passign}{\rho}
\newcommand{\uassign}{{\cal U}}
\newcommand{\modelset}{{\cal M}}

\newcommand{\indegree}{\textrm{indegree}}
\newcommand{\outdegree}{\textrm{outdegree}}
\newcommand{\validate}{\textsf{validate}}

\newcommand{\makenode}[1]{\mathbf{#1}}
\newcommand{\nodeu}{\makenode{u}}
\newcommand{\nodev}{\makenode{v}}
\newcommand{\nodes}{\makenode{s}}
\newcommand{\nodep}{\makenode{p}}
\newcommand{\noder}{\makenode{r}}

\newcommand{\simplify}[2]{#1|_{#2}}
\newcommand{\prov}{\mathit{Prov}}

\newcommand{\progname}[1]{\textsc{#1}}
\newcommand{\dfour}{\progname{d4}}
\newcommand{\Dfour}{\progname{d4}}
\newcommand{\generator}{\progname{d2p}}
\newcommand{\Generator}{\progname{d2p}}
\newcommand{\checker}{\progname{crat-check}}
\newcommand{\Checker}{\progname{Crat-check}}

%% Colored hyperlink 
%\newcommand{\cref}[2]{\href{#1}{\color{blue}#2}}
%% Colored hyperlink showing link in TT font
% \newcommand{\chref}[1]{\href{#1}{\small\tt \color{blue}#1}}
\newcommand{\hcref}[1]{\cref{#1}{\small\tt #1}}

\bibliographystyle{plainurl}% the mandatory bibstyle

\title{Certified Knowledge Compilation \\ with Application to Verified Model Counting}

\titlerunning{Certified Knowledge Compilation}

\author{Randal E. Bryant}{Computer Science Department, Carnegie Mellon University, Pittsburgh, PA 15213 USA}{rebryant@cmu.edu}{https://orcid.org/0000-0001-5024-6613}{Supported by NSF grant CCF-2108521}
\author{Wojciech Nawrocki}{Department of Philosophy, Carnegie Mellon University}{wjnawrock@cmu.edu}{https://orcid.org/0000-0002-8839-0618}{}
\author{Jeremy Avigad}{Department of Philosophy, Carnegie Mellon University}{avigad@cmu.edu}{https://orcid.org/0000-0003-1275-315X}{}
\author{Marijn J. H. Heule}{Computer Science Department, Carnegie Mellon University}{marijn@cmu.edu}{https://orcid.org/0000-0002-5587-8801}{Supported by NSF grant CCF-2108521}

\authorrunning{R. E. Bryant, et al} %TODO mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et al.'

%\Copyright{Jane Open Access and Joan R. Public} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

%\ccsdesc[100]{\textcolor{red}{Replace ccsdesc macro with valid one}} %TODO mandatory: Please choose ACM 2012 classifications from https://dl.acm.org/ccs/ccs_flat.cfm

%\keywords{Dummy keyword} %TODO mandatory; please add comma-separated list of keywords

%\category{} %optional, e.g. invited paper

%\funding{(Optional) general funding statement \dots}%optional, to capture a funding statement, which applies to all authors. Please enter author specific funding statements as fifth argument of the \author macro.

%\nolinenumbers %uncomment to disable line numbering

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\EventEditors{John Q. Open and Joan R. Access}
%\EventNoEds{2}
%\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
%\EventShortTitle{CVIT 2016}
%\EventAcronym{CVIT}
%\EventYear{2016}
%\EventDate{December 24--27, 2016}
%\EventLocation{Little Whinging, United Kingdom}
%\EventLogo{}
%\SeriesVolume{42}
%\ArticleNo{23}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\program}[1]{\textsc{#1}}
\newcommand{\lean}{\program{lean4}}

@@

\section*{Methodology}
\begin{enumerate}
   \item Retrieved 200 public model counting benchmarks from 2022 Model Counting Competition website
     \begin{center}
       \hcref{https://mccompetition.org/2022/mc-description.html}
     \end{center}
     \begin{itemize}
     \item 100 public instances from Track 1 (unweighted model counting)
     \item 100 public instances from Track 2 (weighted model counting)
     \end{itemize}
   \item Removed duplicates
     \begin{itemize}
    \item  20 instances were duplicated in the two tracks
     \item Reduces set of benchmarks to 180
     \end{itemize}
   \item Ran D4 on 180 instances with time limit of 4000 seconds
     \begin{itemize}
     \item Completed for 124 instances
     \end{itemize}
   \item Generated POG representations from dDNNF graphs
     \begin{itemize}
     \item Simplifications via constant propagation
       \begin{itemize}
       \item Number of POG nodes around $0{.}90\times$ number of dDNNF nodes
       \end{itemize}
     \item Used heuristics to identify root node, and then put in topological order with root node at end.
     \item Measure complexity by number of defining clauses $D$
       \begin{itemize}
       \item Product or sum node with degree $k$ requires $k+1$ clauses
       \item $D$ also equals sum of number of edges and number of nodes
       \item For 124 instances, Min = 304, Median = 848,784, Mean = 93,107,937, Max = 2,761,457,765
       \end{itemize}
     \end{itemize}
   \item Ran program {\sc d2p} to generate CRAT file for maximum of 10,000 seconds
     \begin{itemize}
     \item Completed for 108 instances
     \item Exceeded clause limit for 1 instance (Our programs represent a clause ID as a 32-bit signed value)
     \item Ran out of memory for 1 instance
     \item Timed out for 14 instances
     \end{itemize}
   \item For completed CRAT files, ran {\sc crat-check} CRAT checker
     \begin{itemize}
     \item Tests all conditions for correct CRAT
     \item Most time spent performing RUP checks for clause addition and deletion
     \item Completed successfully for all 108 instances
     \item Time generally faster than {\sc d2p}. (min = 0.005, max = 1.4, harmonic mean = 0.10)
     \end{itemize}
\end{enumerate}

@@

\section{Comparison with MICE}

\begin{figure}
\centering{%
\begin{tikzpicture}[scale = 1.00]
  \begin{axis}[mark options={scale=0.55},grid=both, grid style={black!10}, ymode=log, ymin=0.01, ymax=1000,
                              x post scale=2.0, y post scale=2.2,
                              xmode=log,xmin=0.01,xmax=100,
                              xtick={0.01, 0.1,1.0,10,100}, xticklabels={0.01, 0.1, 1.0, 10, 100},
                              ytick={0.01, 0.1,1.0,10,100,1000}, yticklabels={0.01, 0.1, 1.0, 10, 100, {1,000}},
                              xlabel={CRAT total time (seconds)}, ylabel={MICE total time (seconds)},
            ]
    \addplot[mark=none, color=lightblue] coordinates{(0.1,0.01) (10000.0,1000.0)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,0.01) (10000.0,10000.0)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,0.1) (10000,100000)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,1.0) (1000,100000)};
    \addplot[mark=none, color=lightblue] coordinates{(0.01,10.0) (1000,1000000)};
    \input{data-formatted/time-mice-compare}
    \node[left] at (axis cs: 0.9,0.12) {$0{.}1\times$};
    \node[left] at (axis cs: 0.09,0.12) {$1\times$};
    \node[left] at (axis cs: 0.09,1.2) {$10\times$};
    \node[left] at (axis cs: 0.09,12.0) {$100\times$};
    \node[left] at (axis cs: 0.09,120.0) {$1000\times$};

          \end{axis}
\end{tikzpicture}
} % centering
\caption{Running Time for MICE versus CRAT proof chains}
\label{fig:mice}
\end{figure}
